Network Visualizations in \MakeLowercase{\texttt{ggplot2}}

### 2015-10-11 inst/paper.Rnw
if cruvature is specified, geom_curve rather than geom_segment is used for edges

# source code for geom_net
ggplot(data = blood$edges, aes(from_id = from, to_id = to)) +
  geom_net(colour="darkred", layout="circle", label=TRUE, size=15,
           directed=TRUE, vjust=0.5, labelcolour="grey80",
           arrowsize=1.5, linewidth=0.75, arrowgap=0.05) + theme_net()
@

>>>>

# source code for geom_net
ggplot(data = blood$edges, aes(from_id = from, to_id = to)) +
  geom_net(colour="darkred", layout="circle", label=TRUE, size=15,
           directed=TRUE, vjust=0.5, labelcolour="grey80", curvature=0,
           arrowsize=1.5, linewidth=0.75, arrowgap=0.05) + theme_net()
@
